\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://apoorv.me}{\Large APOORV CHATURVEDI}} & Email: \href{mailto:apoorv375@gmail.com}{apoorv375@gmail.com}\\
  \href{https://www.linkedin.com/in/apoorvchaturvedi}{\small linkedin.com/in/apoorvchaturvedi} & Mobile: \href{tel:+917905535463}{+91-7905535463} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
  \small{Results-driven Front-End Developer with 4+ years of experience in crafting responsive and intuitive web designs, specializing in React/Angular.js and Node.js ecosystems. Proven ability to lead development efforts, mentor junior talent, and optimize web applications for enhanced performance and user engagement.}

%-----------SKILLS-----------------
\section{Skills}
\small \textbf{Technical Skills:} HTML5, CSS3, Python, React JS, Angular, GIT, React Native, JavaScript, SEO \\
\small \textbf{Soft Skills:} Creativity, Adaptability, Communication, Problem Solving, Decision making

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KPMG India}{Jan 2022 -- Present}
      {Senior Software Developer}{Gurgaon, India}
      \resumeItemListStart
        \item \small{Spearheaded front-end development for critical web applications, ensuring high performance and responsiveness across various platforms.}
        \item \small{Collaborated closely with cross-functional teams to define requirements and implement innovative UI/UX solutions, improving user satisfaction by 15\%.}
        \item \small{Contributed to architectural decisions for new features, enhancing scalability and maintainability of codebase.}
      \resumeItemListEnd
    \resumeSubheading
      {AdsRole}{Oct 2021 -- Dec 2021}
      {Technical Content Writer}{Remote}
      \resumeItemListStart
        \item \small{Produced high-quality technical documentation and articles, simplifying complex concepts for a broad audience.}
        \item \small{Researched and integrated SEO best practices into content, increasing organic search traffic by 20\% for targeted keywords.}
      \resumeItemListEnd
    \resumeSubheading
      {IndiaMART InterMESH Limited}{Sep 2019 -- Sep 2021}
      {Associate Software Engineer}{Noida, India}
      \resumeItemListStart
        \item \small{Developed and maintained robust front-end components using modern web technologies, contributing to 3 major product releases.}
        \item \small{Participated in code reviews and provided constructive feedback, improving code quality by 10\% within the team.}
        \item \small{Resolved critical bugs and optimized existing features, enhancing application stability and user experience.}
      \resumeItemListEnd
    \resumeSubheading
      {SportsCafe}{July 2018 -- Aug 2018}
      {Software Intern}{New Delhi, India}
      \resumeItemListStart
        \item \small{Assisted senior developers in various software development tasks, gaining hands-on experience with front-end technologies.}
        \item \small{Contributed to minor bug fixes and feature enhancements under guidance, reducing reported issues by 5\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{B2B Work Force}
      {\small Led front-end development efforts, significantly contributing to the analysis, design, development, and integration of B2B web applications. Maintained internal React/Angular.js and Node.js applications, automating quality checks and reducing quality error rates by 15\%.}
    \resumeSubItem{Energy and Petrochemicals}
      {\small Designed and developed a responsive website using HTML5, CSS3, and JavaScript, collaborating with cross-functional teams to implement 5+ new features and enhance user engagement by 10\%.}
    \resumeSubItem{Commercial Finance}
      {\small Collaborated with project management and design teams to deliver responsive, mobile-ready websites using HTML5, CSS3, and JavaScript, improving mobile accessibility by 25\%. Conducted thorough requirements analysis for new web projects, ensuring alignment with client needs and streamlining framework adoption, reducing rework by 8\%.}
    \resumeSubItem{Business Training and Enterprise Risk}
      {\small Partnered with business analysts to translate complex requirements into actionable implementation details, accelerating project initiation by 10\%. Mentored 3 junior developers, improving team productivity by 15\% and fostering knowledge sharing sessions. Streamlined issue clarification and prioritization for business analysts, enhancing inter-team communication by 20\% and reducing defects by 12\%.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harcourt Butler Technological Institute}{Kanpur, India}
      {B.Tech in Computer Science; Percentage: 76\%}{2015 -- 2019}
    \resumeSubheading
      {H.A.L School Korwa}{Amethi, India}
      {Senior Secondary; Percentage: 74.2\%}{2013 -- 2015}
    \resumeSubheading
      {H.A.L School Korwa}{Amethi, India}
      {Secondary; CGPA: 9.0}{2011 -- 2013}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \resumeItemListStart
    \item \small{Front End Web Developer by W3C.}
    \item \small{2021 Microsoft Excel from Udemy.}
    \item \small{General Assembly Web Development.}
  \resumeItemListEnd

\end{document}