\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e} % For \RaggedRight
\usepackage{titlesec} % For custom section titles
\usepackage{enumitem} % For custom list environments
\usepackage{hyperref} % For links
\usepackage{xcolor} % For colors
\usepackage{fontawesome5} % For icons

% Margins
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry}

% Set hyperlink colors for a professional look
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    citecolor=black,
}

% --- Custom commands and formatting ---
% Section titles: bold, large, uppercase, followed by a rule
\titleformat{\section}{\vspace{-4pt}\normalfont\Large\bfseries\color{black}}{}{0em}{\MakeUppercase}[\vspace{-2pt}\rule{\linewidth}{0.8pt}]
\titlespacing{\section}{0pt}{10pt}{0pt} % Spacing for section titles

% Itemize environment for compact lists
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt}

\pagestyle{empty} % No page numbers

\begin{document}

% --- Contact Information ---
\begin{center}
    \textbf{\Huge John Doe} \\
    \vspace{2pt}
    \normalsize City, State \quad \textperiodcentered \quad (XXX) XXX-XXXX \quad \textperiodcentered \quad \href{mailto:your.email@example.com}{your.email@example.com} \quad \textperiodcentered \quad \href{https://linkedin.com/in/yourprofile}{\faLinkedinSquare \ linkedin.com/in/yourprofile}
\end{center}
\vspace{-10pt} % Adjust spacing after contact info

% --- Professional Summary ---
\section*{Professional Summary}
Software Engineer with a strong academic background (GPA: 3.8) and practical experience in developing scalable web applications. Proficient in a wide range of modern technologies including Python, JavaScript, React, Node.js, and AWS. Adept at designing high-performance systems and resolving complex technical issues, with a proven ability to deliver robust software solutions. Seeking to leverage strong problem-solving skills and full-stack development expertise to contribute to innovative projects and drive technological advancements.
\vspace{-5pt} % Adjust spacing as needed

% --- Experience ---
\section*{Experience}
\textbf{Tech Company} \hfill City, State \\
Software Engineer \hfill Jun 2023 – Present
\begin{itemize}
    \item Engineered and maintained scalable web applications using React.js and Node.js, enhancing user engagement and reducing page load times by 15\%.
    \item Designed and implemented high-performance backend APIs with Node.js and PostgreSQL, successfully supporting over \textbf{10,000 concurrent users} with minimal latency.
    \item Collaborated effectively with cross-functional teams following Agile/Scrum methodologies, contributing to the on-time delivery of 5+ major software releases.
    \item Identified and resolved complex technical issues within distributed systems, improving overall system performance and stability by 20\%.
\end{itemize}
\vspace{-5pt} % Adjust spacing as needed

% --- Education ---
\section*{Education}
\textbf{University Name} \hfill City, State \\
Bachelor of Science in Computer Science; GPA: 3.8 \hfill Aug 2019 – May 2023
\vspace{-5pt} % Adjust spacing as needed

% --- Projects ---
\section*{Projects}
\begin{itemize}
    \item \textbf{Portfolio Website:} Engineered a responsive front-end portfolio using React.js and custom CSS, attracting 500+ unique visitors within the first month to showcase personal projects.
    \item \textbf{Task Management App:} Developed a full-stack task management application using the MERN (MongoDB, Express.js, React.js, Node.js) stack, featuring secure user authentication via JWT and comprehensive CRUD functionalities.
\end{itemize}
\vspace{-5pt} % Adjust spacing as needed

% --- Skills ---
\section*{Skills}
\begin{itemize}
    \item \textbf{Languages:} Python, JavaScript, Java, C++
    \item \textbf{Technologies:} MongoDB, React, Node.js, AWS, PostgreSQL, Git, CI/CD
    \item \textbf{Methodologies:} DevOps, Scrum, Agile
\end{itemize}

\end{document}