\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \END{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://arkarn.github.io/}{\Large Ashish Ranjan Karn}} & Email: \href{mailto:ark.iitkgp@gmail.com}{ark.iitkgp@gmail.com}\\
  \href{https://arkarn.github.io/}{arkarn.github.io} & Mobile: \href{tel:+6588893094}{+65 88893094} \\
\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
  \small{
  Highly accomplished Lead Data Scientist with 6+ years of experience in AI, Machine Learning, and Generative AI (GenAI). Proven track record of developing and deploying complex data-driven solutions, including recommendation systems, forecasting models, and large language model applications. AWS Certified ML Specialist adept at leveraging cloud platforms and advanced analytics to drive significant business impact and operational efficiency. Seeking to apply expertise in a challenging environment to solve complex data science problems.
  }

%-----------TECHNICAL SKILLS & CERTIFICATIONS-----------------
\section{Technical Skills \& Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages/Platforms}
      {Python, SQL, C++, Golang, MATLAB, AWS services, Azure services, SAP Cloud Platform}
    \resumeSubItem{Frameworks \& Packages}
      {Langchain, MultiAgent (CrewAI/LangGraph), Spark, Airflow, TensorFlow, MLFlow}
    \resumeSubItem{Knowledge Areas}
      {AI (LLMs, RAG), Machine Learning, Statistics, Deep Learning, Time-series forecasting}
    \resumeSubItem{Certifications}
      {AWS Certified Machine Learning Specialty (MLS-C01), Microsoft Certified Azure Data Scientist (DP-100), Neural Networks and Deep Learning by deeplearning.ai}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
      {Master’s \& Bachelor’s in Electrical Engineering (Signal Processing); CGPA: 8.54/10}{July 2012 -- May 2017}
    \resumeSubheading
      {Delhi Public School RK Puram}{Delhi, India}
      {Senior Secondary (CBSE); Marks: 93\%}{July 2010 -- May 2012}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Grab Holdings Inc.}{Singapore}
      {Lead Data Scientist, Business \& Transactions Platform Team}{Oct 2019 -- Present}
      \resumeItemListStart
        \resumeItem{GenAI/Chatbot}
          {Developed Merchant AI Chatbot with agent capabilities and SSE streaming; integrated chat insights pipeline for analytics, RAG pipeline, and MCP Toolstore enabling cross-team tool hosting.}
        \resumeItem{Recommendation Systems}
          {Developed Central Recommendation System using Multi-Armed Bandit models for contextual recommendations, enhancing Merchant AI Chatbot capabilities; built competitor benchmarking and rating-based models for dynamic optimization.}
        \resumeItem{Accessibility/ESG}
          {Developed Accessibility bot using OpenAI STT \& TTS for 11,000+ visually impaired users in South-East Asia, enabling voice interaction with the Grab app to drive adoption and support ESG efforts.}
        \resumeItem{Multi-Agent Frameworks}
          {Built internal tool for Product Managers using multi-agent framework (CrewAI, LangGraph) for automated PRD generation; integrated company knowledge base (RAG), web-based deep research, JIRA creation, and slide deck generation.}
        \resumeItem{LLM/GPT Classification}
          {Developed high-precision (88\%) classification model for Large Order prediction; utilized LLM/GPT to estimate item attributes from names, descriptions \& prices, significantly reducing cancellations and improving driver allocation.}
        \resumeItem{Demand Forecasting}
          {Achieved accurate demand forecasting (WMAPE of 33\%) for 100k+ fast-selling Grab Mart items, enabling efficient procurement, especially during promos/offers rollout.}
        \resumeItem{ETA/FPT Prediction}
          {Led food delivery ETA/Food prep time prediction framework, improving total ETA prediction accuracy from 72\% to 81\% (Patented: WO2022245295A2, WO2024005708A1, WO2023091078A1) by implementing Batching buffer models using real-time driver supply/demand characteristics; improved Food Preparation Time (FPT) prediction from 62\% to 77\%, enabling Just-In-Time allocation.}
        \resumeItem{Tech Stack}
          {Utilized Python, PySpark, SQL, Airflow, AWS, MLFlow, Kubernetes, GenAI (LLMs, LangChain, CrewAI) for solution development and deployment.}
      \resumeItemListEnd
    \resumeSubheading
      {SAP Labs Pvt. Ltd.}{Bangalore, India}
      {Data Scientist, Innovative Business Solutions (IBSo)}{July 2017 -- Sept 2019}
      \resumeItemListStart
        \resumeItem{Optimization Algorithm}
          {Developed & patented (US20210095559A1) a custom optimization algorithm for oil well rig scheduling, increasing oil production by 6.2\%.}
        \resumeItem{Time-series Forecasting}
          {Built a time-series forecasting API for retail inventory, achieving 8\% MAPE using XGBoost/ARIMA.}
        \resumeItem{Image Classification}
          {Developed an image classification model for an online fashion store, achieving a strong Hamming score of 65\% for multi-label classification across 350 classes and 1M samples by fine-tuning a 16-layer CNN.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Entrepreneurial Endeavors \& Side Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Ringer AI}
      {Creator of AI-Powered Voice Agents for Customer Service.}
    \resumeSubItem{DataSquare.in}
      {Founder of a dormant startup focused on teaching, mentoring, and selling online courses in ML/AI/Analytics domains.}
    \resumeSubItem{ncert.fun}
      {Developed a Q\&A bot leveraging knowledge base specific to NCERT curriculum.}
  \resumeSubHeadingListEnd

\end{document}