\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://arkarn.github.io/}{\Large Ashish Ranjan Karn}} & Email: \href{mailto:ark.iitkgp@gmail.com}{ark.iitkgp@gmail.com}\\
  \href{http://arkarn.github.io/}{arkarn.github.io} & Mobile: \href{tel:+6588893094}{+65 88893094} \\
\end{tabular*}

%-----------PROFESSIONAL SUMMARY-----------------
\section{Professional Summary}
\small{Highly accomplished Lead Data Scientist with over 7 years of experience specializing in applying advanced AI/ML, GenAI, and statistical modeling to solve complex business problems. AWS Certified Machine Learning Specialist with a proven track record in developing and deploying scalable data solutions, optimizing operations, and driving significant business impact through innovative predictive and generative AI models.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
      {Master’s \& Bachelor’s in Electrical Engineering (Signal Processing); CGPA: 8.54/10}{July 2012 -- May 2017}
    \resumeSubheading
      {Delhi Public School RK Puram}{Delhi, India}
      {Senior Secondary (CBSE); Marks: 93\%}{July 2010 -- May 2012}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Grab Holdings Inc.}{Singapore}
      {Lead Data Scientist, Business \& Transactions Platform Team}{Oct 2019 -- Present}
      \resumeItemListStart
        \resumeItem{GenAI / Chatbot Development}
          {Developed Merchant AI Chatbot with agent capabilities and SSE streaming. Integrated chat insights pipeline for analytics, RAG pipeline and MCP Toolstore that enables cross-team tool hosting to enhance agent capabilities.}
        \resumeItem{Recommendation Systems}
          {Developed Central Recommendation System using Multi-Armed Bandit models for contextual recommendations used by Merchant AI Chatbot. Built competitor benchmarking and rating-based models for dynamic optimization.}
        \resumeItem{Voice AI / ESG Initiative}
          {Developed Accessibility bot for 11,000+ visually impaired users in South-East Asia, enabling voice interaction (OpenAI STT \& TTS) with the Grab app; to drive adoption and support company-wide ESG efforts.}
        \resumeItem{Multi-Agent Systems}
          {Built internal tool for Product Managers using multi-agent framework (CrewAI, LangGraph) for PRD generation; integrated company knowledge base (RAG) and Web based deep research, automated JIRA creation and slide deck.}
        \resumeItem{Predictive Modeling}
          {Developed high-precision (88\%) classification model for Large Order prediction; used LLM/GPT to estimate item attributes from names, descriptions \& prices, reducing cancellations and improving driver allocation.}
        \resumeItem{Time-Series Forecasting}
          {Optimized procurement strategies by improving demand forecasting accuracy for Grab Mart items, achieving a Weighted Mean Absolute Percentage Error (WMAPE) of 33\% over 100k fast-selling items, particularly beneficial during promos/offers.}
        \resumeItem{ETA Optimization}
          {Led food delivery ETA/Food prep time prediction framework; improved total ETA prediction accuracy from 72\% to 81\% by implementing Batching buffer model using real-time driver supply demand characteristics; improved Food Preparation time (FPT) prediction from 62\% to 77\% that helped enable Just-In-Time allocation.}
        \resumeItem{Technical Proficiency}
          {Tech stack: Python, PySpark, SQL, Airflow, AWS, MLFlow, Kubernetes, GenAI (LLMs, LangChain, CrewAI).}
      \resumeItemListEnd
    \resumeSubheading
      {SAP Labs Pvt. Ltd.}{Bangalore, India}
      {Data Scientist, Innovative Business Solutions (IBSo)}{July 2017 -- Sept 2019}
      \resumeItemListStart
        \resumeItem{Optimization Algorithms}
          {Developed \& patented a custom optimization algorithm for oil well rig scheduling, increasing oil production by 6.2\%.}
        \resumeItem{API Development}
          {Built a time-series forecasting API for retail inventory, achieving 8\% MAPE using XGBoost/ARIMA.}
        \resumeItem{Deep Learning}
          {Developed an image classification model for online fashion store client; multi-label classification belonging to 350 classes and a million sample input; fine tuned CNN with 16 layers to achieve hamming score of 65\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS & CERTIFICATIONS-----------------
\section{Technical Skills \& Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages/Platforms}{Python, SQL, C++, Golang, MATLAB, AWS services, Azure services, SAP Cloud Platform}
    \resumeSubItem{Frameworks \& Packages}{Langchain, MultiAgent (CrewAI/LangGraph), Spark, Airflow, TensorFlow, MLFlow}
    \resumeSubItem{Knowledge Areas}{AI (LLMs, RAG), Machine Learning, Statistics, Deep Learning, Time-series forecasting}
    \resumeSubItem{Certifications}{\textbf{AWS Certified Machine Learning Specialty (MLS-C01)}; \textbf{Microsoft Certified Azure Data Scientist (DP-100)}; Neural Networks and Deep Learning by deeplearning.ai; Other relevant certifications link}
  \resumeSubHeadingListEnd

%-----------PATENTS-----------------
\section{Patents}
  \resumeSubHeadingListStart
    \resumeSubItem{US20210095559A1}{Workover rig scheduling to maximize oil production for onshore oil fields}
    \resumeSubItem{WO2022245295A2}{System and method for predicting delivery time for batch orders}
    \resumeSubItem{WO2024005708A1}{Service request estimated time generation system and method}
    \resumeSubItem{WO2023091078A1}{Dynamic Padding Buffer Time Optimisation for Food ETA Prediction}
  \resumeSubHeadingListEnd

%-----------ENTREPRENEURIAL ENDEAVORS & SIDE PROJECTS-----------------
\section{Entrepreneurial Endeavors \& Side Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Ringer AI}{Developed an AI-powered voice agent solution for customer service, leveraging advanced natural language processing and voice synthesis technologies.}
    \resumeSubItem{DataSquare.in}{Founded an educational platform providing online courses and mentorship in Machine Learning, AI, and Analytics, reaching aspiring professionals.}
    \resumeSubItem{Other Side Projects}{Developed various AI/ML projects including a QnA Bot, Drowsiness Detector, Audio-to-Image synthesis, and ncert.fun, exploring diverse applications of AI.}
  \resumeSubHeadingListEnd

\end{document}