\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize]}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{mailto:sweet.prerna4@gmail.com}{\Large PRERNA}} & Email: \href{mailto:sweet.prerna4@gmail.com}{sweet.prerna4@gmail.com}\\
  {} & Mobile: \href{tel:+919986690005}{+91 9986690005} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\small{Proven ability to function as a Strategic HR Business Partner and develop and implement successful human resources management strategies to support corporate mandate. Action-oriented and performance-driven individual offering exceptional communication and Analytics skills. Achieves results through relationship building and collaboration at all levels of organization and externally to source, recruit, develop and retain diverse talent and sustain employee engagement.}
\vspace{10pt} % Add some space after summary

%-----------SKILLS-----------------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item
    \small{\textbf{HR Expertise:} Strategic HR Business Partnering, End-to-End Recruitment, Onboarding & Orientation, Employee Engagement, Grievance Redressal, Performance Management (PIP Programs, Appraisals), Leave Management, Training & Development, Payroll Management, Attrition Analysis & Retention, Stakeholder Management, Talent Engagement, Succession Planning, Compensation Benchmarking, Client Acquisition.}
    \item
    \small{\textbf{Tools & Technologies:} Proficient in various HRIS and ATS platforms (e.g., Workday, SAP SuccessFactors), HR Analytics tools, Microsoft Office Suite (Excel, Word, PowerPoint).}
    \item
    \small{\textbf{Soft Skills:} Leadership, Effective Communication, Problem-solving, Adaptability, Detail-oriented, Compassionate, Empathetic, Positive Attitude, Team Player, Relationship Building, Collaboration.}
  \end{itemize}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Affine Analytics}{Bangalore}
      {Strategic HR Business Partner}{Feb 2016 -- Present}
      \resumeItemListStart
        \resumeItem{Onboarding & Engagement}{Ensured smooth Onboarding and Orientation process for over 400 new hires, reducing time-to-productivity and fostering early engagement.}
        \resumeItem{HR Projects Leadership}{Handled and led major HR Projects including PIP Programs, Leave Management, Training & Development, and Performance Appraisals, optimizing HR processes and enhancing employee experience.}
        \resumeItem{Retention Management}{Collaborated with Management on Attrition Analysis and developed Retention Management Programs, contributing to improved employee retention.}
        \resumeItem{Payroll Management}{Managed end-to-end Payroll for over 400 employees across diverse geographies, ensuring accuracy and compliance.}
        \resumeItem{Strategic HR Advisory}{Translated business needs into actionable HR services, delivering people-based solutions that directly supported business objectives and growth.}
        \resumeItem{Recruitment Leadership}{Oversaw the complete end-to-end Recruitment Process, successfully hiring over 400 employees; mentored and guided a team to maximize their potential.}
        \resumeItem{Stakeholder Management}{Managed key stakeholders to understand resource requirements across different clients and domains, ensuring timely talent acquisition.}
        \resumeItem{Talent Management}{Engaged with teams on critical talent issues, including talent engagement, succession planning, and compensation benchmarking.}
        \resumeItem{Recruitment Drives}{Organized and managed large-scale recruitment drives with footfalls exceeding 200 candidates per event, efficiently building talent pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {Enigma GR}{Bangalore}
      {Senior Recruitment Consultant}{Jul 2015 -- Feb 2016}
      \resumeItemListStart
        \resumeItem{Recruitment Management}{Managed complete end-to-end recruitment for middle to senior management positions, successfully placing professionals across various domains for Fortune 100 clients.}
        \resumeItem{Client Acquisition}{Involved in Client Acquisition, proactively identifying client needs and adopting strategic hiring methods to secure new business partnerships.}
      \resumeItemListEnd

    \resumeSubheading
      {Kelly Services India Pvt. Ltd}{Bangalore}
      {Recruitment Consultant}{Feb 2013 -- Jun 2015}
      \resumeItemListStart
        \resumeItem{Specialized Recruitment}{Accountable for end-to-end recruitment across all levels within the Analytics & Consulting domain, covering Credit Risk, Retail Banking, Marketing Analytics, Sales Analytics, Project/Program Management, Predictive Analytics, and Data Science roles.}
        \resumeItem{Team Mentorship}{Managed and mentored a recruitment team, enhancing their understanding of Analytics skills and client requirements to improve placement efficiency.}
        \resumeItem{Candidate Management}{Conducted benchmarking, screening/interviewing, and candidate selection; proficiently negotiated compensation and set realistic candidate expectations.}
      \resumeItemListEnd

    \resumeSubheading
      {Asterion Consulting Pvt. Ltd.}{Bangalore}
      {Talent Acquisition Executive}{Jul 2011 -- Jan 2013}
      \resumeItemListStart
        \resumeItem{Analytics Recruitment}{Involved in hiring Analytics professionals across various domains, contributing to talent acquisition goals.}
        \resumeItem{Client Relationship Management}{Managed client relationships to understand recruitment needs and ensure alignment with business objectives.}
        \resumeItem{Sourcing & Networking}{Developed and leveraged professional networks to source candidates and gather references, optimizing candidate pipelines.}
        \resumeItem{Recruitment Strategy}{Understood and implemented appropriate recruitment strategies for each requirement, selecting suitable channels for talent outreach.}
        \resumeItem{Interview Coordination}{Scheduled shortlisted candidates and ensured their attendance at interview venues, streamlining the hiring process.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International School of Business & Research}{Bangalore}
      {Masters’ in Business Administration - HR}{2009 -- 2011}
    \resumeSubheading
      {Patna Women’s College}{Patna}
      {Bachelors’ in Business Administration}{2006 -- 2009}
    \resumeSubheading
      {Patna Women’s College}{Patna}
      {Intermediate in Arts}{2004 -- 2006}
    \resumeSubheading
      {International School}{Patna}
      {Matriculation - I.C.S.E.}{2004}
  \resumeSubHeadingListEnd

%-----------EXTRA-CURRICULAR / PROJECTS-----------------
\section{Projects \& Activities}
  \resumeSubHeadingListStart
    \resumeSubItem{Traffic Awareness Camps}{Conducted Traffic Awareness Camps in Bangalore as part of an E-WEEK activity in 2010 at ISBR, Bangalore, promoting community safety.}
    \resumeSubItem{CSR Education Initiative}{Provided education to a government primary school in Bangalore as a CSR Activity, collaborating with NEN in 2009 at ISBR, Bangalore, supporting local community development.}
    \resumeSubItem{LST Competition}{Participated and ranked among the top 20 investors in the LST competition at an inter-college level in 2009 at ISBR, Bangalore, demonstrating analytical and strategic thinking.}
  \resumeSubHeadingListEnd

\end{document}