\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsNames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://arkarn.github.io/}{\Large Ashish Ranjan Karn}} & Email: \href{mailto:ark.iitkgp@gmail.com}{ark.iitkgp@gmail.com}\\
  \href{https://arkarn.github.io/}{arkarn.github.io} & Mobile: \href{tel:+6588893094}{+65 88893094} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\small{Highly accomplished Lead Data Scientist with 7+ years of experience specializing in advanced Machine Learning, Generative AI, and MLOps. Proven track record of delivering impactful data-driven solutions, including developing cutting-edge GenAI applications, optimizing complex operations (e.g., 6.2\% oil production increase), and enhancing user experiences for over 11,000 visually impaired users. Adept at leading complex projects, building scalable systems, and driving significant business outcomes through innovation and technical excellence.}

%-----------SKILLS-----------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item
    \textbf{Generative AI \& LLMs}{: LLMs, RAG, Multi-Agent Frameworks (CrewAI, LangGraph), LangChain} \\
    \textbf{Machine Learning}{: Deep Learning, Time-series Forecasting, MLOps (MLFlow, Kubernetes), XGBoost, ARIMA, TensorFlow, Spark} \\
    \textbf{Programming Languages}{: Python, SQL, PySpark, C++, Golang, MATLAB} \\
    \textbf{Cloud Platforms}{: AWS services, Azure services, SAP Cloud Platform} \\
    \textbf{Tools & Frameworks}{: Airflow, MLFlow, Kubernetes, Spark, TensorFlow, LangChain, CrewAI, LangGraph} \\
    \textbf{Knowledge Areas}{: AI, Machine Learning, Statistics, Deep Learning, Time-series forecasting} \\
    \textbf{Certifications}{: AWS Certified Machine Learning Specialty (MLS-C01), Microsoft Certified Azure Data Scientist (DP-100), Neural Networks and Deep Learning by deeplearning.ai}
    }
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
      {Masters and Bachelors in Electrical Engineering (Signal Processing); CGPA: 8.54/10}{July 2012 -- May 2017}
    \resumeSubheading
      {Delhi Public School RK Puram}{Delhi, India}
      {Senior Secondary (CBSE); Marks: 93\%}{July 2010 -- May 2012}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Grab Holdings Inc.}{Singapore}
      {Lead Data Scientist, Business and Transactions Platform Team}{Oct 2019 -- Present}
      \resumeItemListStart
        \resumeItem{Generative AI}
          {Developed a Merchant AI Chatbot with agent capabilities and SSE streaming; integrated chat insights pipeline for analytics, RAG pipeline, and MCP Toolstore to enhance agent capabilities and cross-team tool hosting.}
        \resumeItem{Machine Learning}
          {Built a Central Recommendation System using Multi-Armed Bandit models for contextual recommendations, improving Merchant AI Chatbot effectiveness; included competitor benchmarking and rating-based models for dynamic optimization.}
        \resumeItem{Generative AI}
          {Engineered an Accessibility bot using OpenAI STT and TTS, enabling voice interaction for over 11,000 visually impaired users across South-East Asia, significantly increasing app adoption and supporting company-wide ESG efforts.}
        \resumeItem{Multi-Agent Frameworks}
          {Developed an internal multi-agent tool (CrewAI, LangGraph) for Product Managers, automating PRD generation by integrating company knowledge base (RAG) and web-based deep research, also automating JIRA creation and slide deck generation, saving significant PM time.}
        \resumeItem{LLM / ML}
          {Achieved 88\% precision with a classification model for Large Order prediction, utilizing LLM/GPT to estimate item attributes from names, descriptions, and prices, thereby reducing cancellations and optimizing driver allocation.}
        \resumeItem{Time-series Forecasting}
          {Ensured accurate demand forecasting for Grab Mart items, helping operations in efficient procurement during promos/offers rollout, achieving WMAPE of 33\% across 100k fast-selling items.}
        \resumeItem{MLOps / Optimization}
          {Led the food delivery ETA/Food prep time prediction framework, improving total ETA prediction accuracy from 72\% to 81\% by implementing Batching buffer model using real-time driver supply-demand characteristics; improved Food Preparation Time (FPT) prediction from 62\% to 77\%, enabling Just-In-Time allocation.}
      \resumeItemListEnd
    \resumeSubheading
      {SAP Labs Pvt. Ltd.}{Bangalore, India}
      {Data Scientist, Innovative Business Solutions (IBSo)}{July 2017 -- Sept 2019}
      \resumeItemListStart
        \resumeItem{Optimization}
          {Developed and patented a custom optimization algorithm for oil well rig scheduling, directly increasing oil production by 6.2\%.}
        \resumeItem{Time-series Forecasting}
          {Built a time-series forecasting API for retail inventory, achieving 8\% MAPE using XGBoost/ARIMA, enhancing inventory management efficiency.}
        \resumeItem{Deep Learning}
          {Developed an image classification model for an online fashion store client, performing multi-label classification across 350 classes with a million sample input; fine-tuned a 16-layer CNN to achieve a Hamming score of 65\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Ringer AI}
      {AI-Powered Voice Agents for Customer Service.}
    \resumeSubItem{DataSquare.in}
      {Dormant startup focused on teaching, mentoring, and selling online courses in ML/AI/Analytics domain.}
    \resumeSubItem{Other Side Projects}
      {QnA Bot, Drowsiness Detector, Audio-to-Image, ncert.fun.}
  \resumeSubHeadingListEnd

%-----------PATENTS-----------------
\section{Patents}
  \resumeSubHeadingListStart
    \resumeSubItem{US20210095559A1}
      {Workover rig scheduling to maximize oil production for onshore oil fields.}
    \resumeSubItem{WO2022245295A2}
      {System and method for predicting delivery time for batch orders.}
    \resumeSubItem{WO2024005708A1}
      {Service request estimated time generation system and method.}
    \resumeSubItem{WO2023091078A1}
      {Dynamic Padding Buffer Time Optimisation for Food ETA Prediction.}
  \resumeSubHeadingListEnd

\end{document}