\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://arkarn.github.io/}{\Large Ashish Ranjan Karn}} & Email: \href{mailto:ark.iitkgp@gmail.com}{ark.iitkgp@gmail.com}\\
  \href{https://arkarn.github.io/}{arkarn.github.io} & Mobile: \href{tel:+6588893094}{+65 88893094} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
  \small{Lead Data Scientist with 7+ years of experience leading the development and deployment of advanced Machine Learning, Generative AI, and MLOps solutions, consistently driving significant business outcomes. Proven track record of delivering impactful data-driven solutions, including developing cutting-edge GenAI applications, optimizing complex operations (e.g., 6.2\% oil production increase), and enhancing user experiences for over 11,000 visually impaired users. Adept at leading complex projects, building scalable systems, and driving significant business outcomes through innovation and technical excellence.}

%-----------SKILLS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{Python, SQL, C++, Golang, MATLAB}
    \resumeSubItem{AI \& Machine Learning}{Deep Learning, Time-series Forecasting, LLMs, RAG, Statistics}
    \resumeSubItem{MLOps & Big Data}{MLFlow, Kubernetes, Spark, Airflow}
    \resumeSubItem{Cloud Platforms}{AWS, Azure, SAP Cloud Platform}
    \resumeSubItem{Frameworks & Libraries}{LangChain, CrewAI, LangGraph, PySpark, TensorFlow, XGBoost, ARIMA}
    \resumeSubItem{Certifications}{AWS Certified Machine Learning Specialty (MLS-C01), Microsoft Certified Azure Data Scientist (DP-100), Neural Networks and Deep Learning by deeplearning.ai}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology (IIT) Kharagpur}{Kharagpur, India}
      {Masters and Bachelors in Electrical Engineering (Signal Processing); CGPA: 8.54/10}{July 2012 -- May 2017}
    \resumeSubheading
      {Delhi Public School RK Puram}{Delhi, India}
      {Senior Secondary (CBSE); Marks: 93\%}{July 2010 -- May 2012}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Grab Holdings Inc.}{Singapore}
      {Lead Data Scientist, Business and Transactions Platform Team}{Oct 2019 -- Present}
      \resumeItemListStart
        \resumeItem{Generative AI}{Developed Merchant AI Chatbot with agent capabilities and SSE streaming; integrated chat insights, RAG pipeline, and MCP Toolstore to enable cross-team tool hosting, enhancing agent efficiency and data-driven insights.}
        \resumeItem{Recommendation Systems}{Developed Central Recommendation System using Multi-Armed Bandit models for contextual recommendations used by Merchant AI Chatbot; built competitor benchmarking and rating-based models for dynamic optimization.}
        \resumeItem{Accessibility/GenAI}{Developed Accessibility bot for 11,000+ visually impaired users in South-East Asia, enabling voice interaction (OpenAI STT and TTS) with the Grab app, resulting in increased adoption and supporting company-wide ESG efforts.}
        \resumeItem{Automation/GenAI}{Built an internal multi-agent framework tool (CrewAI, LangGraph) for Product Managers, automating PRD generation, JIRA creation, and slide decks by integrating company knowledge base and web research, significantly streamlining product development workflows and accelerating time-to-market.}
        \resumeItem{LLM/Classification}{Developed high-precision (88\%) classification model for Large Order prediction, using LLM/GPT to estimate item attributes from names, descriptions, and prices, reducing cancellations and improving driver allocation.}
        \resumeItem{Time-series Forecasting}{Achieved accurate demand forecasting for Grab Mart items, helping operations team in efficient procurement, especially during promos/offers rollout; achieved WMAPE = 33\% over 100k fast-selling items.}
        \resumeItem{Predictive Modeling}{Led food delivery ETA/Food prep time prediction framework, improving total ETA prediction accuracy from 72\% to 81\% by implementing Batching buffer model using real-time driver supply demand characteristics; improved Food Preparation Time (FPT) prediction from 62\% to 77\% that helped enable Just-In-Time allocation.}
        \resumeItem{Tech Stack}{Utilized Python, PySpark, SQL, Airflow, AWS, MLFlow, Kubernetes, and GenAI technologies (LLMs, LangChain, CrewAI) across projects.}
      \resumeItemListEnd
    \resumeSubheading
      {SAP Labs Pvt. Ltd.}{Bangalore, India}
      {Data Scientist, Innovative Business Solutions (IBSo)}{July 2017 -- Sept 2019}
      \resumeItemListStart
        \resumeItem{Optimization}{Developed and patented a custom optimization algorithm for oil well rig scheduling, increasing oil production by 6.2\%.}
        \resumeItem{Time-series Forecasting}{Built a time-series forecasting API for retail inventory, achieving 8\% MAPE using XGBoost/ARIMA.}
        \resumeItem{Image Classification}{Developed an image classification model for an online fashion store client; multi-label classification belonging to 350 classes and a million sample input; fine tuned CNN with 16 layers to achieve hamming score of 65\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Ringer AI}{Developed AI-Powered Voice Agents for customer service, leveraging advanced natural language processing and voice technologies.}
    \resumeSubItem{DataSquare.in (dormant startup)}{Co-founded DataSquare.in, a dormant startup focused on teaching, mentoring, and selling online courses in ML/AI/Analytics domains, fostering knowledge dissemination.}
    \resumeSubItem{Other Side Projects}{Explored various side projects including a QnA Chatbot, Drowsiness Detector, Audio-to-Image generation, and ncert.fun, demonstrating diverse technical interests and rapid prototyping abilities.}
  \resumeSubHeadingListEnd

%-----------PATENTS-----------------
\section{Patents}
  \resumeSubHeadingListStart
    \resumeSubItem{US20210095559A1}{Workover rig scheduling to maximize oil production for onshore oil fields}
    \resumeSubItem{WO2022245295A2}{System and method for predicting delivery time for batch orders}
    \resumeSubItem{WO2024005708A1}{Service request estimated time generation system and method}
    \resumeSubItem{WO2023091078A1}{Dynamic Padding Buffer Time Optimisation for Food ETA Prediction}
  \resumeSubHeadingListEnd

\end{document}